Type cones of $\b{g}$-vector fans

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
corrected setting

\noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
We that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, Ext-finite, and has Auslander--Reiten--Serre duality.

@@

We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.  Thus is has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.  This gives a setting in which to apply Theorem~\ref{}.

>>>>

\noindent {\bf Setting for Section~\ref{sect::Statment extricats}}
In that section, we keep the previous setting, but assume moreover that~$\cat$ is Krull--Schmidt, $\field$-linear, Ext-finite, and has Auslander--Reiten--Serre duality, and that the subcategory~$\tc$ is of the form~$\add T$, where~$T=T_1\oplus\cdots\oplus T_n$ is a basic object.

@@

We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.  Thus it has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.  This gives a setting in which to apply Theorem~\ref{}.
